\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-10 paper_resources/doc/paper.tex
CD plots: description updated

\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}

@@

\begin{figure}[H]

@@

In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}. Note that in this case the exact percentage of each problem instance is given w.r.t.\  10 separately executed runs on that instance.

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there. \fxnote{Marko: update of the content needed.}

\begin{itemize}
	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.  The second best ranking is achieved by \textsc{AI-Feynman} algorithm. There is no statistically significant difference between these two approaches. However, these two approaches perform statistically significantly better than the third best (according the the average raking), that is with \textsc{Apf-Fe}. This conclusion also holds for the remaining approaches, which are performing statistically significantly weaker than  \textsc{Rils}-\textsc{Rols} method. 
	\item    Concerning the instance problems with the included level of noise of 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.   The second best ranking is achieved by \textsc{Afp-Fe} algorithm. However,  there is no statistically significant difference between these two approaches. The third best approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically significantly worse that our \textsc{Rils}-\textsc{Rols} method. For all remaining methods, the later conclusion also holds.
	\item   Concerning the instance problems in the presence of the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking; the second best approach is \textsc{gplearn}. The difference between the exact percentages delivered by these two approaches is statistically significant in favor of \textsc{Rils-Rols} approach. This also holds when \textsc{Rils-Rols} is compared to all the remaining approaches.

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
		\caption{No noise}
		\label{fig:CDplots-no-noise}
	\end{subfigure}

>>>>

In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}. Note that the exact percentage of each problem instance that comes into the statistical observation is given as the average of  10 separately executed runs for that instance.

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In each CD plot, the (15) competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there.

\begin{itemize}
	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of   exact percentage rate.  The second best ranking is achieved by \textsc{AI-Feynman} algorithm. There is no statistically significant difference between these two approaches w.r.t.\ obtained exact percentages. However, these two approaches perform statistically significantly better than the third best approach according the the average raking, \textsc{Apf-Fe}. This conclusion also holds for the remaining approaches, which are performing statistically significantly worse than  \textsc{Rils}-\textsc{Rols} method. 
	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.   The second best ranking is achieved by \textsc{AI-Feynman} algorithm. However,  there is no statistically significant difference between these two approaches. The third best approach is \textsc{Afp-Fe} which perform statistically equal to \textsc{Afp} and \textsc{AI-Feynman}, but statistically significantly worse than our \textsc{Rils}-\textsc{Rols} method. For all remaining approaches,  \textsc{Rils}--\textsc{Rols} performs statistically better in terms of obtained exact percentages.
	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking according to obtained exact percentages; the second best approach is \textsc{Afp-Fe} and \textsc{Afp}. These latter three approaches perform statistically equal. 
	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is tied to \textsc{gplearn}. The the exact percentages obtained by the latter two approaches are statistically worse than those of the \textsc{Rils}--\textsc{Rols} method.  This also holds when \textsc{Rils-Rols} is compared to all   remaining approaches.

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
		\caption{No noise}
		\label{fig:CDplots-no-noise}
	\end{subfigure}

\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}\label{sec:scalability-rils-rols}

@@

@@
